---
output: github_document
language: en
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
Sys.setlocale("LC_TIME", "en_US.UTF-8")  # En anglais

```

# stockr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stockr)](https://CRAN.R-project.org/package=stockr)
<!-- badges: end -->

`stockr` is an R package that retrieve financial data from Yahoo Finance, in order to provide historic of financial values and helper functions.

> `stockr` functions return a standardized *`data.frame`* with consistent column names, allowing you to focus directly on financial analysis.

**Main functions.**

```{r fn, echo=FALSE}
fn <- data.frame(Minimal.example = c("`stockr::get_historic('SAAB-B.ST')`", "`stockr::get_changes('USD', 'EUR')`","`stockr::get_info_from_name('Saab')`", "`stockr::get_indices()`" ) 
                 , Input = c("Ticker symbol(s)^[https://en.wikipedia.org/wiki/Ticker_symbol]", "Currencies to convert : from value(s) to value(s)"
                             , "Free-text(s), e.g., company name(s)" , "")
             , Return =  c("Daily historic of financial data*", "Latest exchange rates*"
                           ,"Ticker symbol(s) and companie(s) that match the text searched, and latest financial insights^†^" , "Major world financial indices and their actual values^‡^")
          
)

knitr::kable(fn, format = "markdown", caption = "Sources : <br>* : Yahoo Finance API, e.g., https://query1.finance.yahoo.com/v1/finance/currencies <br>† : Scraping from https://finance.yahoo.com/lookup/  <br>‡ : Scraping from https://finance.yahoo.com/markets/world-indices/")

```
   
          
## Installation

You can install the development version of stockr:

``` r
devtools::install_github("clement-LVD/stockr")
```

## Examples

**Get ticker symbol and actual values.** Given keyword(s) such companies names, search latest stock values with `stockr::get_info_from_name`.

```{r example}
library(stockr)

swed_indices <- stockr::get_info_from_name(names = c("SAAB", "VOLVO"))

str(swed_indices) # Results of the day, over all marketplaces
```

If you don't know the ticker symbol of a financial value, `stockr::get_info_from_name` is a way to retrieving it.

**Get historical financial data.**  Given ticker symbol(s), get historic of financial values with `stockr::get_historic` :

```{r example2}

# Fetch historical values, given ticker symbol(s)
histo <- stockr::get_historic(symbols = c("SAAB-B.ST", "VOLV-B.ST"), .verbose = FALSE)

str(histo)

```

Each lines of this `data.frame` are daily values.

**Change currencies** See Vignette of [`stockr::get_changes()`](https://clement-lvd.github.io/stockr/articles/Get_changes.html)
 

