---
title: "get_info_and_historic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_info_and_historic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette show how to fetch data from company names and get historic financial data from Yahoo API.

```{r setup}
library(stockr)
```

Fetch ticker symbols associated with keyword(s) such as companies names, and get historical financial data for these symbols. 

```{r example3}
# 1) fetch_indices (optionally filter a precise marketplace)
indices <- stockr::get_info_from_name(names = c("VOLVO", "RENAULT")
                         , exchange = "STO")
# Keep only the swedish exchange place (STOckholm)

# 2) Fetch historical values, given ticker symbol(s)
datas <- stockr::get_historic(symbols = indices$symbol)

str(datas)
```

## Technical details

**Role of stockr in the 'Reach Yahoo Finance from R' ecosystem.** Regarding the historical financial values associated with a ticker symbol returned by other packages such as `quantmod` and `yahoofinancer` : they have all the same source as `stockr`, i.e. Yahoo Finance API. Therefore, the returned objects have different properties, see below. 

```{r echo=FALSE}

deps <- data.frame(names = c("stockr", "yahoofinancer", "quantmod")
  
, get_historic = c("`stockr::get_historic()` return a standard `data.frame`",
                 "`yahoofinancer` methods return an `R6` class object (e.g., `Ticker$get_history`)"
                 , "`quantmod::getSymbols()` return a time.series (`xts` & `zoo` object)" ) )

knitr::kable(deps, row.names = F)


```

<!--Other packages are partially redundant with `stockr` : `quantmod` and `yahoofinancer`. `stockr` have : -->

<!--   - the minimal amount of dependencies in this ecosystem -->
<!--   - a free-text search function, i.e. `stockr::get_info_from_name()`. -->

<!-- Therefore, other packages certainly offer more functions, e.g., `quantmod` offers time series data visualization methods.  -->
